Multi-fluids for Representing Sub-filter-scale Convection

### 2020-04-06 submit2/manuscript.tex
First draft responding to reviewer comments

\change[HW}{This paper presents solutions of the multi-fluid Boussinesq equations for convection, reproducing aspects of highly resolved dry convection
at coarse horizontal resolution.}
{This paper presents solutions of the two-fluid Boussinesq equations using coarse horizontal resolution (one column) which reproduce aspects of highly resolved single-fluid simulations of dry, two-dimensional convection.}
Two test cases are used to \change[HW]{validate}{evaluate}
the multi-fluid model. The first is a Boussinesq version of the well
known two dimensional dry rising bubble of \citeA{BF02} and the second
is a dry two dimensional version of radiative-convective equilibrium
with heating at the ground and uniform radiative cooling. High resolution
single-fluid simulations are coditionally averaged based on the sign
of vertical velocity ($w$) in order to \change[HW]{create}{define} rising and falling
fluids which each have their own mean buoyancy, velocity and pressure.
The two-fluid, \change[HW]{single}{one} column Boussinesq model reproduces mean vertical
heat and mass transport of these test cases.

@@

\change{A set of unknowns in the multi-fluid equations are the}{The} properties of the fluid that are transferred from one fluid to another \add[HW]{are unknowns in the multi-fluid equations that require closure}. An obvious
first guess would be that fluid takes its mean buoyancy and velocity
with it when it is transferred. However sub-\change{grid}{filter}-scale variability
of each fluid means that we expect that the most buoyant fluid will
be transferred to the rising fluid or the fluid with the largest vertical
velocity will be transferred to the rising fluid and vice versa. An
accurate estimate of these would depend on knowledge of the sub-grid-scale
variability of each fluid which we do not have. Instead we assume
that the fluid transferred in each direction has zero vertical velocity
which is consistent with our conditional averaging. We have tested
three models for the buoyancy of the fluid transferred. The most successful
is to assume that the fluid takes its mean buoyancy with it. Assuming
that the buoyancy of the transferred fluid is an average of the buoyancy
of both fluids can lead to unrealistically large or small, unbounded
buoyancies. Similarly, if we assume that one fluid has negative buoyancy
and the other positive buoyancy and we transfer fluid of zero buoyancy,
then unbounded buoyancy can occur. A better model of the buoyancy
of the fluid transferred would rely on more information the sub-grid-scale
variability.

\change[HW]{Single}{One} column multi-fluid modelling with moisture has already been
demonstrated by \citeA{TEB19} 
\add[HW]{and two dimensional simulations of the multi-fluid Euler equations by \protect\citeA{WM19} }.
Two important next steps are to simulate
convection in the grey zone (where it is partially resolved) and to
represent sub-grid-scale variability within each fluid by solving
multi-fluid prognostic equations for turbulent kinetic energy and
other moments of the sub-grid variability. These can be used to inform
cloud base mass flux (since only the most buoyant fluid will transfer
from the stable environment to the buoyant plume) and inform models
of the properties of the fluid that is transferred. This will lead
to a unified parameterisation of turbulence and convection and will
take multi-fluid modelling of convection beyond existing paradigms.

>>>>

\change[HW]{This paper presents solutions of the multi-fluid Boussinesq equations for convection, reproducing aspects of highly resolved dry convection
at coarse horizontal resolution.}
{This paper presents solutions of the two-fluid Boussinesq equations using coarse horizontal resolution (one column) which reproduce aspects of highly resolved single-fluid simulations of dry, two-dimensional convection.}
Two test cases are used to \change[HW]{validate}{evaluate}
the multi-fluid model. The first is a Boussinesq version of the well
known two dimensional dry rising bubble of \citeA{BF02} and the second
is a dry two dimensional version of radiative-convective equilibrium
with heating at the ground and uniform radiative cooling. High resolution
single-fluid simulations are coditionally averaged based on the sign
of vertical velocity ($w$) in order to \change[HW]{create}{define} rising and falling
fluids which each have their own mean buoyancy, velocity and pressure.
The two-fluid, \change[HW]{single}{one} column Boussinesq model reproduces mean vertical
heat and mass transport of these test cases.

@@

\change{A set of unknowns in the multi-fluid equations are the}{The} properties of the fluid that are transferred from one fluid to another \add[HW]{are unknowns in the multi-fluid equations that require closure}. An obvious
first guess would be that fluid takes its mean buoyancy and velocity
with it when it is transferred.
\change[HW]{However sub-grid-scale variability
of each fluid means that we expect that the most buoyant fluid will
be transferred to the rising fluid or the fluid with the largest vertical
velocity will be transferred to the rising fluid and vice versa. An accurate estimate of these would depend on knowledge of the sub-grid-scale
variability of each fluid which we do not have. Instead we assume
that the fluid transferred in each direction has zero vertical velocity
which is consistent with our conditional averaging.}
{Improvements on this assumption will depend on knowledge of sub-filter-scale variablity. However since conditional averaging is on $w$, it is consistent to assume that the fluid transferred has $w=0$.}
\remove[HW]{We have tested}
Three models for the buoyancy of the fluid transferred 
\add[HW]{are proposed}. The most successful
is to assume that the fluid takes its mean buoyancy with it. Assuming
that the buoyancy of the transferred fluid is an average of the buoyancy
of both fluids can lead to unrealistically large or small, unbounded
buoyancies. 
\change[HW]{Similarly, if we assume}{Assuming}
that one fluid has negative buoyancy and the other positive buoyancy and 
\remove[HW]{we transfer}
fluid of zero buoyancy \add[HW]{is transferred},
then unbounded buoyancy can occur. A better model of the buoyancy
of the fluid transferred would rely on more information \add[HW]{of} the
sub-\change[HW]{grid}{filter}-scale variability.

\change[HW]{Single}{One} column multi-fluid modelling with moisture has already been demonstrated by \citeA{TEB19} 
\add[HW]{and two dimensional simulations of the multi-fluid Euler equations by \protect\citeA{WM19} }.
Two important next steps are to simulate convection in the grey zone (where it is partially resolved) and to represent sub-\change[HW]{grid}{filter}-scale variability within each fluid by solving multi-fluid prognostic equations for turbulent kinetic energy and other moments of the sub-\change[HW]{grid}{filter} variability. 
\remove[HW]{These can be used to inform}
Cloud base mass flux \add[HW]{could then be estimated based on higher-order moments of the vertical velocity and buoyancy within the environment fluid.}
\remove{(since only the most buoyant fluid will transfer
from the stable environment to the buoyant plume) and inform models
of the properties of the fluid that is transferred.}
This will lead
to a unified parameterisation of turbulence and convection and will
take multi-fluid modelling of convection beyond existing paradigms.
